Active Transfer Learning

### 2018-03-16 paper/paper.tex
Edits to the writeup 4

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{bm}
\usepackage{todonotes}

@@

@@

>>>>

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{bm}
\usepackage{todonotes}
\usepackage{algorithm}
\usepackage{algorithmic}

@@

\renewcommand{\algorithmicrequire}{\textbf{Input:}}
\renewcommand{\algorithmicensure}{\textbf{Output:}}

@@

Finally, we show how to compute the gradient and the Hessian of $||\widetilde{B}(\bm{w})||_D^2$ with respect to $\bm{w}$ when we use a linear model $Q_{\bm{w}}(s,a) = \bm{w}^T\bm{\phi}(s,a)$. Let $y_i(\bm{w}) = r_i + \gamma\mm_{a'}\bm{w}^T\bm{\phi}(s_i',a')$. The gradient can be computed as:
\begin{align}
\nabla_{\bm{w}_k} ||\widetilde{B}(\bm{w})||_D^2 =\ & 
\frac{1}{N}\sum_{i=1}^N \nabla_{\bm{w}_k} \left( y_i(\bm{w}) - \bm{w}^T\bm{\phi}(s_i,a_i) \right)^2 \\ =\ &
\frac{2}{N}\sum_{i=1}^N \left( y_i(\bm{w}) - \bm{w}^T\bm{\phi}(s_i,a_i) \right)\left( \nabla_{\bm{w}_k}y_i(\bm{w}) - \nabla_{\bm{w}_k}\bm{w}^T\bm{\phi}(s_i,a_i)) \right) \\ =\ &
\frac{2}{N}\sum_{i=1}^N \left( y_i(\bm{w}) - \bm{w}^T\bm{\phi}(s_i,a_i) \right)\left( \gamma\nabla_{\bm{w}_k}\mm_{a'}\bm{w}^T\bm{\phi}(s_i',a') - \phi_k(s_i,a_i)) \right) \\ =\ &
\frac{2}{N}\sum_{i=1}^N \left( y_i(\bm{w}) - \bm{w}^T\bm{\phi}(s_i,a_i) \right)\left( \gamma\frac{\sum_{a'} e^{\kappa \bm{w}^T\bm{\phi}(s_i',a')} \phi_k(s_i',a'))}{\sum_{a'} e^{\kappa \bm{w}^T\bm{\phi}(s_i',a')}} - \phi_k(s_i,a_i)) \right)
\end{align}
Similarly, the diagonal of the Hessian is:
\begin{align}
\nabla_{\bm{w}_k,\bm{w}_k}^2 ||\widetilde{B}(\bm{w})||_D^2 =\ & 
\frac{1}{N}\sum_{i=1}^N \nabla_{\bm{w}_k,\bm{w}_k}^2 \left( y_i(\bm{w}) - \bm{w}^T\bm{\phi}(s_i,a_i) \right)^2 \\ =\ &
\frac{2}{N}\sum_{i=1}^N \nabla_{\bm{w}_k} \left( y_i(\bm{w}) - \bm{w}^T\bm{\phi}(s_i,a_i) \right)\left( \gamma\frac{\sum_{a'} e^{\kappa \bm{w}^T\bm{\phi}(s_i',a')} \phi_k(s_i',a'))}{\sum_{a'} e^{\kappa \bm{w}^T\bm{\phi}(s_i',a')}} - \phi_k(s_i,a_i)) \right) \\ =\ &
\frac{2}{N}\sum_{i=1}^N \left( \gamma\frac{\sum_{a'} e^{\kappa \bm{w}^T\bm{\phi}(s_i',a')} \phi_k(s_i',a'))}{\sum_{a'} e^{\kappa \bm{w}^T\bm{\phi}(s_i',a')}} - \phi_k(s_i,a_i)) \right)^2 \\ \ \ & - \frac{2\kappa}{N}\sum_{i=1}^N \left( y_i(\bm{w}) - \bm{w}^T\bm{\phi}(s_i,a_i) \right) \frac{\left(\sum_{a'} e^{\kappa \bm{w}^T\bm{\phi}(s_i',a')} \phi_k(s_i',a'))\right)^2}{\left(\sum_{a'} e^{\kappa \bm{w}^T\bm{\phi}(s_i',a')}\right)^2}
\end{align}

We are now ready to present our algorithm for transfer-based exploration via posterior sampling. This is shown in Alg. \ref{alg:transfer}.

\begin{algorithm}
\begin{algorithmic}
\REQUIRE Prior mean $\bar{\bm{\mu}}$, prior covariance $\bar{\bm{\Sigma}}$, likelihood weight $\lambda$, mellowmax parameter $\kappa$, learning rate $\eta$, feature vector $\bm{\phi}$
\ENSURE Greedy policy $\pi$
\\\hrulefill

\STATE{Initialize posterior: $\bm{\mu} \leftarrow \bar{\bm{\mu}}, \bm{\Sigma} \leftarrow \bar{\bm{\Sigma}}$}
\STATE{Initialize dataset: $D = \emptyset$}
\REPEAT

\STATE{Sample $Q$-function: $\bm{w} \sim \mathcal{N}(\bm{\mu},\bm{\Sigma})$}
\STATE{Sample initial state: $s_0 \sim p_0$}

\FOR{$h=0,\dots,H$}
\STATE{Take action $a_h = \argmax_a \bm{w}^T\bm{\phi}(s_h,a)$}
\STATE{Observe transition $s_{h+1} \sim \mathcal{P}(\cdot | s_h,a_h)$}
\STATE{Collect reward $r_h = \mathcal{R}(s_h,a_h)$}
\STATE{Add sample to the dataset: $D \leftarrow D \cup \langle s_h,a_h,r_h,s_{h+1} \rangle$}
\STATE{Compute ELBO: $\mathcal{L}(\bm{\mu},\bm{\Sigma}) = \mathbb{E}_{\bm{w} \sim \mathcal{N}(\bm{\mu},\bm{\Sigma})}\left[ \lambda N ||\widetilde{B}(\bm{w})||_{D}^2 \right] + KL(\mathcal{N}(\bm{\mu},\bm{\Sigma})\ ||\ \mathcal{N}(\bar{\bm{\mu}},\bar{\bm{\Sigma}}))$}
\STATE{Compute gradients $\nabla_{\bm{\mu}}\mathcal{L}(\bm{\mu},\bm{\Sigma})$ and $\nabla_{\bm{\Sigma}}\mathcal{L}(\bm{\mu},\bm{\Sigma})$}
\STATE{Update posterior parameters: $\bm{\mu} \leftarrow \bm{\mu} - \eta\nabla_{\bm{\mu}}\mathcal{L}(\bm{\mu},\bm{\Sigma})$ and $\bm{\Sigma} \leftarrow \bm{\Sigma} - \eta\nabla_{\bm{\Sigma}}\mathcal{L}(\bm{\mu},\bm{\Sigma})$}
\ENDFOR

\UNTIL{done}
\STATE{Sample final parameters: $\bm{w}^* \sim \mathcal{N}(\bm{\mu},\bm{\Sigma})$ (or take the MAP: $\bm{w}^* = \bm{\mu}$)}
\RETURN{Greedy policy: $\pi(s) = \argmax_a \bm{w}^* \bm{\phi}(s,a)$}
\end{algorithmic}
\caption{Variational Exploration under Gaussian Approximation} \label{alg:transfer}
\end{algorithm}
